Deep mutational scanning of hemagglutinin helps distinguish the evolutionary fate of human H3N2 influenza virus lineages

### 2018-01-05 paper/manuscript.tex
Added Sanger seq supp fig to manuscript

We mutagenized the entire HA coding sequence at the codon level to create mutant plasmid libraries harboring an average of $\sim$1.4 codon mutations per clone (\comment{supplementary figure with Sanger sequencing}).
We then generated mutant virus libraries from the mutant plasmids using a helper-virus system that enables the efficient generation of complex influenza virus libraries~\cite{doud2016accurate} (Figure~\ref{fig:dms_overview}A).
These mutant viruses derived all of their non-HA genes from the lab-adapted WSN/1933 strain.
Using WSN/1933 for the non-HA genes reduces biosafety concerns, and also helped increase viral titers.
To further increase viral titers, we used MDCK-SIAT1 cells that we had engineered to constitutively express the TMPRSS2 protease, which facilitates HA cleavage and activation~\cite{bottcher2006proteolytic, bottcher2010cleavage}.

@@

>>>>

We mutagenized the entire HA coding sequence at the codon level to create mutant plasmid libraries harboring an average of $\sim$1.4 codon mutations per clone (Figure~\ref{suppfig:SangerSeq}).
We then generated mutant virus libraries from the mutant plasmids using a helper-virus system that enables the efficient generation of complex influenza virus libraries~\cite{doud2016accurate} (Figure~\ref{fig:dms_overview}A).
These mutant viruses derived all of their non-HA genes from the lab-adapted WSN/1933 strain.
Using WSN/1933 for the non-HA genes reduces biosafety concerns, and also helped increase viral titers.
To further increase viral titers, we used MDCK-SIAT1 cells that we had engineered to constitutively express the TMPRSS2 protease, which facilitates HA cleavage and activation~\cite{bottcher2006proteolytic, bottcher2010cleavage}.

@@

\begin{suppfigure}
\centerline{\includegraphics[width=\textwidth]{figs/S02_SangerSeq/SangerSeq.pdf}}
\caption{\label{suppfig:SangerSeq}
{\bf Sanger sequencing of 30 clones from the mutant plasmid libraries.} 
(A) 
(B)
(C)
(D)
(E)
}
\end{suppfigure}
